Epistemic Semantics in Guarded String Models

### 2020-06-17 tex/draft.tex
add description of P

Rather than individual guarded strings, elements of a guarded string
model for KAT are sets of guarded strings.  In the application, these
elements have the interpretation of propositions (sets of possible
worlds) and/or event types.  An event such as $u$ in the guarded
string model corresponds to the set of guarded strings where the bare
event is flanked by compatible atoms. In standard KATs, this is  as defined in an Epik
program by the event declaration and the constraint declaration.
These have the status of event types, in that they can ``happen'' in
different possible worlds. Here happening corresponds to incrementing
the world with some compatible element of the event type.  Where $e$
is a bare event symbol, $\llbracket e \rrbracket^{\varphi,P}$ is the
corresponding set of guarded strings, consisting of the bare event
decorated with compatible truth assignments denoted by $P$ that are
admitted by the world-constraints $\varphi$.  See this formally in
Figure~\ref{fig:interp}, and the examples in \ex{events1}.
% u (!q!p):(!qp) + (!qp):(q!p) + (q!p):(qp) 173
% d (!qp):(!q!p) + (q!p):(!qp) + (qp):(q!p)

\begin{example} \label{events1}
\(
\begin{array}[t]{l|c}
  e & \llbracket e \rrbracket^{\varphi, P} \\ \hline  
  u & \{ \hat 0 ~u~ \hat 1, \hat 1 ~u~ \hat 2,  \hat 2 ~u~ \hat 3\}\\
  d & \{ \hat 1 ~d~ \hat 0, \hat 2~d~\hat 1, \hat 3 ~d~ \hat 2\}\\
  a_1 & \{H ~a_1~ H\}\\
  a_0 & \{T ~a_0~ T\}\\
  b_1 & \{H ~b_1~ H \}\\
  b_0 & \{T ~b_0~ T \}
\end{array}
\)
\end{example}

>>>>

Rather than individual guarded strings, elements of a guarded string
model for KAT are sets of guarded strings.  In the application, these
elements have the interpretation of propositions (sets of possible
worlds) and/or event types.  An event such as $u$ in the guarded
string model corresponds to the set of guarded strings where the bare
event is flanked by compatible atoms. In standard KATs, every possible
atom is allowed to surround every event, which leads to nonsensical
strings like $\hat 1 ~u~\hat 0$ in the denotation of $u$, indicating
that the elevator travelled up from floor 1 to floor 0 (a physical
impossibility).

Fortunately, Epik provides a syntax to specify the input-output
behavior via the \texttt{event} declarations. From these we construct
a function $P$ from agents to relations on atoms that specify the
effects each action can have. If there are multiple event declarations
for the same event, only the latter one is incorporated. To construct
the effect relation $P(e)$ for event $e$, we add a pair $\alpha,
\beta$ to the relation $P(e)$ for every disjunct $\phi:\phi'$ such
that $\alpha \models \phi$ and $\beta \models \phi'$.  These have the
status of event types, in that they can ``happen'' in different
possible worlds. Here happening corresponds to incrementing the world
with some compatible element of the event type.  Where $e$ is a bare
event symbol, $\llbracket e \rrbracket^{\varphi,P}$ is the
corresponding set of guarded strings, consisting of the bare event
decorated with compatible truth assignments denoted by $P$ that are
admitted by the world-constraints $\varphi$.  See this formally in
Figure~\ref{fig:interp}, and the examples in \ex{events1}.
% u (!q!p):(!qp) + (!qp):(q!p) + (q!p):(qp) 173
% d (!qp):(!q!p) + (q!p):(!qp) + (qp):(q!p)

\begin{example} \label{events1}
  \renewcommand{\arraystretch}{1.1}
\(
\begin{array}[t]{l|c}
  e & \llbracket e \rrbracket^{\varphi, P} \\ \hline
  u & \{ \hat 0 ~u~ \hat 1, \hat 1 ~u~ \hat 2,  \hat 2 ~u~ \hat 3\}\\
  d & \{ \hat 1 ~d~ \hat 0, \hat 2~d~\hat 1, \hat 3 ~d~ \hat 2\}\\
  a_1 & \{H ~a_1~ H\}\\
  a_0 & \{T ~a_0~ T\}\\
  b_1 & \{H ~b_1~ H \}\\
  b_0 & \{T ~b_0~ T \}
\end{array}
\)
  \renewcommand{\arraystretch}{1}

\end{example}
